\begin{thebibliography}{99}

\bibitem{Brown78}
  K.\ Q.\ Brown.
  \newblock{Fast intersection of half spaces.}
  \newblock{Technical Report 15213 (Carnegie-Mellon University,
    1978).}

\bibitem{Chazelle80}
  B.\ Chazelle.
  \newblock{Computional Geometry and Convexity.}
  \newblock{PhD Thesis (Yale University, 1980).}

\bibitem{Chazelle83}
  B.\ Chazelle.
  \newblock{The polygon containment problem.}
  \newblock{\emph{Advances in Computing Research} 1, str. 1--33
    (1983).}

\bibitem{FreeShap75}
  H.\ Freeman, R.\ Shapira.
  \newblock{Determining the minimum-area encasing rectangle for
    an arbitrary closed curve.}
  \newblock{\emph{ Communications of the ACM} 7, str. 409--413
    (1975).}

\bibitem{Graham72}
  R.\ L.\ Graham.
  \newblock{An efficient algorithm for determining the convex hull
    of a finite planar set.}
  \newblock{\emph{Information Processing Letters} 1, str.\ 132--133
    (1972).}

\bibitem{Hersh93}
  J.\ Hershberger, S.\ Suri.
  \newblock{Matrix searching with the shortest path metric.}
  \newblock{\emph{Proceedings of the Twenty-Fifth Annual ACM
      Symposium on Theory of Computing} (STOC 1993), str. 385--494}

\bibitem{HockYou61}
  J.\ G.\ Hocking, G.\ S.\ Young.
  \newblock{Topology.}
  \newblock{Addison-Wesley (1961).}

\bibitem{Kirk83}
  D.\ Kirkpatrick.
  \newblock{Optimal search in planar subdivisions.}
  \newblock{\emph{SIAM Journal on Computing} 12, str. 28--35 (1983).}

\bibitem{Meisters75}
  G.\ H.\ Meisters.
  \newblock{Polygons have ears.}
  \newblock{\emph{American Mathematical Monthly} 6, str. 648--651 (1975).}

\bibitem{Prep85}
  S.\ Preparata, M.\ I.\ Shamos.
  \newblock{Computational Geometry: An Introduction}
  \newblock{Springer-Verlag (1985)}

\bibitem{ShamosHoey76}
  M.\ I.\ Shamos, D.\ Hoey.
  \newblock{Geometric intersection problems.}
  \newblock{\emph{Proceedings of the Seventeeth Annual IEEE Symposium on
      Foundations of Computer Science} (FOCS 1976), str.\ 208--215.}

\bibitem{Toussaint83}
  G.\ T.\ Toussaint.
  \newblock{Solving geometric problems with the rotating calipers.}
  \newblock{Technical Report (McGill University, 1983).}

\bibitem{ToussaintInt}
  G.\ T.\ Toussaint.
  \newblock{A simple linear algorithm for intersecting convex polygons.}
  \newblock{Technical Report H3A 2A7 (McGill University, 1985).}

\bibitem{Orourke98}
  J.\ O'Rourke.
  \newblock{Computional Geometry in C.}
  \newblock{Cambridge University Press~(1998).}

\bibitem{YagBol61}
  I.\ M. Yaglom, V.\ G.\ Boltyanskii.
  \newblock{Convex Figures.}
  \newblock{Hold, Rinehart and Winston (1961).}
\end{thebibliography}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "masterthesis"
%%% TeX-engine: xetex
%%% End:
